\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-07 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
changement texte modèle

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline  
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\ 
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline  
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. }}}
\end{table}

\subsubsection{Reducing international transport costs}

In this first exercise, we contrast the effects of a reduction of international transport costs depending on whether this occurs through a reduction in ad-valorem costs only, or a combined reduction in both the additive and the multiplicative components. In Table \ref{tab:resultats_modele}, this relies on the results reported in Column (A) versus (B) for Air, Column (E) versus (F) for Vessel.\medskip

Whatever the transport mode (and the associated magnitude of the transport costs decrease), welfare gains are higher when this reduction is partly achieved through a reduction of additive costs. The effect is substantial: The reduction of 3.4 percentage points of Air transport costs generates a welfare gain higher by 0.58 percentage point when such a reduction occurs through the additive component (accounting for almost 60\% of the total cost decrease), rather than when it realizes through a decrease in iceberg costs only. In maritime transport, where the decrease in total transport costs is larger (-6.4 percentage points), the extra welfare gain amounts to 1.12 percentage points when the transport cost reduction occurs through the additive component (by 50\%) rather than through the iceberg component only.\smallskip

@@

\subsubsection{Reducing fixed export costs}

@@

The answer can be found in Table \ref{tab:resultats_modele}, by comparing Columns (B) to (D) for Air, (F) to (H) for Vessel, the difference between these two columns (for each transport mode) being the lower value of the fixed export cost. Here again, the welfare gains of trade liberalization (under the form of a lower fixed export cost) are larger when variable trade costs involve a part of additive costs: If the effect are quantitatively modest in maritime transport (by 0.75 percentage points, from 3.3\% to 4.05\%), the decrease in the fixed export cost is more sizeable when variable costs are lower, as in air transport where the welfare gains almost double (from 1.82\% to 3.25\%).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele_decompwelfare}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
%$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
%$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
%$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
%$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\ \hline
Variety effect (\%)&	-0.827	&0.747	&-2.670&	-1.132	&-1.323	&-0.126&	-3.061	& -1.857 \\
Price effect (\%)&	2.084&	1.455	&5.202&	4.444&	3.568	&3.001&	6.829&	6.059 \\ 
\hline
\end{tabular}
\end{center}
%{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: The reduction in transport costs is expressed in percentage points. }}}
\end{table}

>>>>

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3& 0&	-3.3 \\
$\Delta \mathcal{W}$ & 0,0202 &  0,0386 & 0,0362 & 0,0540 & 0,0354 & 0,0535 & 0,0467 & 	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	2,393 &	2.207	&3,348	&2.179	&3,382 &	2.872&	4.00   \\\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. }}}
\end{table}

\paragraph{Reduction in international variable transport costs}

We first consider the effects of a reduction of variable international transport costs. Specifically, we contrast two different environments: In the first scenario ``\`{a} la M\'{e}litz'', only ad-valorem transport costs apply, which consequently reduce. In the second scenario so called ``\`{a} la Hummels'', international transport costs are made of both additive and ad-valorem costs. The overall transport costs decreases then comes from a reduction in both components. The size of the overall transport costs, as well as their reduction, is identical in both scenarii. We calibrate them in our empirical estimates, considering 1974 and 2019 as initial and final values. They are transport-mode specific. In the scenario ``\`{a} la Hummels'', the initial and finale values of each additive and ad-valorem component is also based on our empirical estimates. Importantly, the size of the overall transport costs decrease is kep identical under both scenarii. What differs is the composition of this decrease. The two scenarii for each transport mode are reported in Table \ref{tab:resultats_modele}.\medskip

A first conclusion emerges. Whatever the transport mode (and the associated magnitude of the transport costs decrease), trade liberalization induces welfare gains. Second, the welfare gains are higher when this reduction is partly achieved through a reduction of additive costs. The effect is substantial: The reduction of 3.4 percentage points of Air transport costs generates a welfare gain higher by 0.58 percentage point when such a reduction occurs through the additive component (accounting for almost 60\% of the total cost decrease), rather than when it realizes through a decrease in iceberg costs only. In maritime transport, where the decrease in total transport costs is larger (-6.4 percentage points), the extra welfare gain amounts to 1.12 percentage points when the transport cost reduction occurs through the additive component (by 50\%) rather than through the iceberg component only.\smallskip

@@

\paragraph{Reduction of the fixed export cost}

@@

The answer can be found in Table \ref{tab:resultats_modele_fx}, by comparing Columns (B) to (D) for Air, (F) to (H) for Vessel, the difference between these two columns (for each transport mode) being the lower value of the fixed export cost. Here again, the welfare gains of trade liberalization (under the form of a lower fixed export cost) are larger when variable trade costs involve a part of additive costs. \textbf{A FINIR ET A CREUSER}

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization (2): Reduction of the fixed export cost} \label{tab:resultats_modele_fx}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
%$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
%$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
%$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
%$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	2.393 &	2.207	&3.348	&2.179	&3.382&	2.872&	4.00   \\ \hline
Variety effect (\%)&	-0.827 	&-2.599	&0.747
&-1.038	&-1.323	& -3.123&	-0.126	&-1.902 \\
Price effect (\%)&	2.084 &5.201	& 1.455 &	4.444&	3.568	& 6.829&	 3.001&	6.059 \\
\hline
\end{tabular}
\end{center}
%{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: The reduction in transport costs is expressed in percentage points. }}}
\end{table}
